I don't know if projection is categorical. \\ Did \citealt{mandelkern-etal2020} discover that it is?

### 2025-04-05 output/naturalness-paper/second-submission/paper.tex
added comments to paper

@@

\noindent
{\bf Keywords:} Presuppositions, categorical vs.\ gradient projection, inference ratings, naturalness ratings in explicit ignorance contexts.

@@

Presuppositions are often characterized as backgrounded content that typically projects out of entailment-canceling environments, like the scope of negation or a polar interrogative (e.g., \citealt{ccmg90}).\footnote{Conventional implicatures also project out of these environments. They differ from presuppositions in that they contribute novel information. For discussion see, e.g., \citealt{ccmg90} and \citealt{potts05}.} Thus, a content like the content of the clausal complement (CC) of {\em know} in (\ref{first}a) is taken to be a presupposition because a speaker who utters (\ref{first}a) is typically taken to believe the CC, that Julian dances salsa, even though the CC occurs in a polar interrogative. By contrast, the CC of {\em think} in (\ref{first}b) is not assumed to be a presupposition because it does not typically project. Accordingly, {\em know} is analyzed as a presupposition trigger, but {\em think} is not.

@@

Many theoretical works assume that projection is a categorical property of  content, that is, content either typically projects (in which case it is a presupposition) or it does not (in which case it is not a presupposition). There is, however, mounting empirical evidence that projection is not a categorical property of  content but rather a gradient one, with content being more or less projective. The measure used to establish this evidence are inference rating measures: Such measures involve presenting participants with an utterance (like (\ref{first}a)) and contents (like that Julian dances salsa), and asking for ratings that are taken to reveal the existence or strength of the inference to the content. \citealt{karttunen71b}, for instance, suggested that the CCs of {\em regret} and {\em discover}, which he took to be presuppositions, exhibit projection variability in examples like (\ref{kart}). Specifically, he suggested that a speaker who utters (\ref{kart}a) believes that the addressee has not told the truth, whereas a speaker who utters (\ref{kart}b) ``is not sure about the truth of the complement'' (p.63).

@@

\citealt[\S6.2]{mandelkern-etal2020} suggested that naturalness ratings of utterances in explicit ignorance contexts are better suited to distinguish presuppositions from nonpresuppositional projection inferences.\footnote{\citealt{mandelkern-etal2020} refer to the measure as an acceptability rating measure, but since participants were asked to rate the naturalness of utterances, we refer to it as a naturalness rating measure.} On this measure, participants are presented with utterances in which a speaker states that they are ignorant about a content, as in (\ref{mtrig}a), and then follows up with an utterance in which the content occurs embedded in an entailment-canceling environment, such as the antecedent of a conditional in (\ref{mtrig}c). \citealt{mandelkern-etal2020} assumed that if the content is a presupposition (such as the pre-state content of {\em stop} in (\ref{mtrig}c)), the utterance is rated as unnatural in the explicit ignorance context because presuppositions are contents that the speaker believes to be true. That is, in such constellations,  participants ``will not have an alternative to interpreting the presupposition at the utterance level, and in turn seeing the utterance as infelicitous and the speaker as incoherent'' (p.497).  If, on the other hand, the content is not a presupposition (such as the pre-state content of {\em now frown on} in (\ref{mtrig}c)), the utterance is assumed to be natural: Even if participants might in some context draw a projection inference ``for any of a variety of pragmatic reasons short of entailment or presupposition, [\ldots] they will tend to relinquish that inclination when there is pragmatic pressure to do so'', as in the explicit ignorance contexts (p.497). Both presupposition triggers and nontriggers were expected to be judged as natural in the support context, which entails the relevant content, illustrated in (\ref{mtrig}b).

@@

However, the empirical evidence in \citealt{mandelkern-etal2020} for their claim that projection is categorical is weak. This is primarily because the goal of their work was not to investigate this claim, but whether presupposition projection in conjunctions is symmetric. It is also weak, however, because the results (shown in Fig.~8 in their Appendix 3) do not appear to support a categorical distinction between the presupposition triggers and nontriggers investigated, even though there were only four triggers ({\em be aware, be happy, stop, continue}) and four nontriggers ({\em now frown on, enjoy, hope, be sure}).  First, considering just the mean naturalness ratings in the explicit ignorance context, it appears that the ratings for the presuppositions and nonpresuppositions overlap: The ratings for the presuppositions ranged from 1 (for the pre-state of {\em continue}) to about 3.5 (for the CC of {\em be aware}), and the ratings for the nonpresuppositions range from just below 3 (for the CC of {\em hope}) to 4.5 (for the CC of {\em be aware}). It is therefore not clear that naturalness ratings in explicit ignorance contexts provide evidence for a categorical distinction between the four presuppositions and the four nonpresuppositions investigated in \citealt{mandelkern-etal2020}. Second, there is no consistent effect of context: Whereas the difference between the mean naturalness ratings in the explicit ignorance and support context was quite large for the (presuppositional) pre-state of {\em continue}, the difference was much less pronounced for the (presuppositional) CC of {\em be aware}, where it was roughly comparable to that of the (nonpresuppositional) pre-state of {\em frown on}. Thus, it is not clear that comparisons of ratings in support and explicit ignorance contexts provides empirical support for a categorical projection either.

@@

This paper presents the results of an experiment designed to investigate \citepos{mandelkern-etal2020} claim that the measure they proposed provides evidence that projection is categorical and distinguishes presuppositions from nonpresuppositions.\footnote{\label{f:github}The experiment was approved by the ethics review committee of [university name suppressed]. The experiment, materials, data, and analysis scripts can be accessed here:  \url{https://anonymous.4open.science/r/naturalness-in-EIC-5847}.}  To allow for comparison with the results of \citealt{degen-tonhauser-language}, the CCs of the same 20 (non)factive clause-embedding predicates (see Fig.~\ref{fig:dt1a}) were investigated. The experiment also included control stimuli with {\em stop, continue, again, too, also}, and an {\em it-}cleft to allow for comparison with the results of \citealt{mandelkern-etal2020} and the assumptions made in \citealt{simons01} and \citealt{abusch10}.

The design of \citepos{mandelkern-etal2020} Exp.~3 was slightly modified to allow for comparison with the result of \citealt{degen-tonhauser-openmind} that the projection of content is sensitive to the content's prior probability. Specifically, what \citealt{degen-tonhauser-openmind} found was that the higher the prior probability of a content, the stronger the projection inference. For instance, a speaker's commitment to the CC of (\ref{prior}c), that Julian dances salsa, was stronger in the context in (\ref{prior}b), where the CC has a higher prior probability, than in the context in (\ref{prior}a), where the CC has a lower prior probability.

@@

In addition to the 1,200 target stimuli (400 interrogatives $\times$ 3 contexts), the materials also included the six control stimuli in (\ref{filler}). The interrogatives of the control stimuli featured six expressions typically analyzed as presupposition triggers, namely {\em stop, continue, again, too, also}, and an {\em it-}cleft. The preceding declaratives conveyed the speaker's explicit ignorance about the presuppositions associated with these expressions.\footnote{The contents investigated for {\em too} and {\em also} in (\ref{filler}d) and (\ref{filler}e) are that Ann plays an instrument other than the flute and that Svenja plays a sport other than soccer. This interpretation arises if {\em too} and {\em also} associate with {\em the flute} and {\em soccer}, respectively. While prosody was not controlled for, this focus association is made plausible by the preceding explicit ignorance statements, which evoke the question of whether Ann plays any instrument and whether Svenja plays any sport, respectively.} Two of these expressions, namely {\em stop} and {\em continue}, were target expressions in \citepos{mandelkern-etal2020} Exp.~3, where they were assumed to be unnatural in explicit ignorance contexts. This is in contrast to \citealt{simons01}, who took {\em stop} to be a soft trigger that is natural in explicit ignorance contexts. Three expressions were assumed to be unnatural in explicit ignorance contexts in \citealt{simons01} ({\em again}) and \citealt{abusch10} ({\em too}, {\em it-}cleft). The control stimuli were included for comparison to the target stimuli, to the claims of \citealt{simons01} and \citealt{abusch10}, and to the results of \citealt{mandelkern-etal2020}.

@@

\paragraph{Results.} Recall that \citealt{simons01} and \citealt{abusch10} assumed that only hard presuppositions are unnatural in explicit ignorance contexts, whereas \citealt{mandelkern-etal2020} assumed that all presuppositions are unnatural in such contexts. Figure \ref{fig:acc-by-expression} shows mean naturalness ratings in the explicit ignorance context by expression (in distinct colors: \color{orange}factive predicates\color{black}, \color{green}nonfactive predicates\color{black},  controls). As shown, the purported presupposition triggers, that is, the controls and the factive predicates, do not exhibit a unified pattern: The means of four controls ({\em continue, too, also, again}) are at floor, those of {\em stop} and {\em be annoyed} are slightly higher, those of the {\em it-}cleft and {\em know} are higher again, but lower than those of {\em see} and {\em discover}, and, finally, those of {\em reveal} are highest. We also see that the naturalness ratings of {\em see, discover} and {\em reveal} are just as high as those of some nonfactive predicates. These results do not provide empirical support for a categorical distinction between presuppositions and nonpresuppositions, contrary to what \citealt{mandelkern-etal2020} claimed. These results also do not provide support for a class of factive predicates that is categorically distinct from nonfactive ones, in line with the result of \citealt{degen-tonhauser-language} based on inference rating measures.

@@

The linking function assumed in \citealt{mandelkern-etal2020} is that presupposition triggers are rated as unnatural in contexts in which the speaker is explicitly ignorant of the presupposed content, and that nontriggers are rated as natural in such contexts. This linking function is challenged by some of the results of our experiment. Consider first the CC of {\em be annoyed}, which received a very low mean naturalness rating in the explicit ignorance context. Under \citepos{mandelkern-etal2020} linking function, one can make sense of this result by analyzing the CC of {\em be annoyed} as being conventionally coded as having to be entailed by or satisfied in the common ground of the interlocutors. It has been long known, however, that such an analysis is not tenable for emotive predicates like {\em be annoyed}, as they do not presuppose that the CC is part of the common ground of the interlocutors but merely that the attitude holder believes the CC to be true (e.g., \citealt{heim92,karttunen2016}). In (\ref{emo}), for instance, the speaker does not believe that Sue could stay in bed.

@@

The results for {\em know} also challenge \citepos{mandelkern-etal2020} linking function. As shown in Fig.~\ref{fig:acc-by-expression}, the naturalness ratings for the CC of {\em know} exhibit a bimodal pattern, with about half of the participants rating it as relatively unnatural in the explicit ignorance context and about half as relatively natural. For the first group of participants, one could assume either that they reacted to the contradiction between the speaker's explicit ignorance statement and the inference arising from the interrogative that the CC projects to the common ground of the interlocutors, or one could assume an analysis along the same lines as for {\em be annoyed} above as the CC of {\em know} is also highly not-at-issue (\citealt{tbd-variability}). For the second group of participants, those who judged speakers' utterances like (\ref{pros}) as fairly natural, one hypothesis is that they read the utterances with a (possibly implicit) prosody that supports an interpretation on which the CC does not project out of the interrogative utterance. Two possible prosodies are indicated by the ToBI transcriptions of in (\ref{pros}); in both, the interrogative is realized with the so-called rise-fall-rise contour.\footnote{ToBI refers to the Tones and Break Indices annotation system of \citealt{beckman-ayers97}. In this system, L*+H identifies a pitch accent whose low target is aligned with the stressed syllable and which is followed by a trailing high target. A L* pitch accent may also be followed by a low (L-) or high (H-) intermediate phrase tone. An intonational phrases may end with a low intermediate phrase tone and a high intonational phrase tone (L-H\%) or a high intermediate and intonational phrase tone (H-H\%).}

@@

As shown, the effect of context is not uniform for the factive predicates. For {\em be annoyed} and {\em know} the mean naturalness rating is quite a bit lower in the explicit ignorance context than in the higher prior probability context, whereas the difference is much less pronounced for {\em see} and {\em discover}, and not observed for {\em reveal}. This last pattern is also observed for several nonfactive predicates, including {\em confess, hear, announce}, and {\em be right}. Thus, naturalness ratings in explicit ignorance vs.\ higher prior probability contexts do not provide support for a categorical distinction between the CCs of factive and nonfactive predicates. A comparison between the explicit ignorance and lower prior probability contexts also suggests differences between the factive predicates: Whereas for {\em be annoyed} the mean naturalness rating is lower in the explicit ignorance context than in the lower prior probability context, the two means are equally high for {\em know}, but the rating in the lower prior probability context is lower than that in the explicit ignorance context for {\em see, discover}, and {\em reveal}. This last pattern is observed for all of the nonfactive predicates. Thus, naturalness ratings in explicit ignorance vs.\ lower prior probability contexts also do not provide support for a categorical distinction between the CCs of factive and nonfactive predicates.

@@

\paragraph{Discussion.} As mentioned above, contemporary presupposition analyses (e.g., \citealt{heim83,vds92}) assume that presuppositions are by default globally accommodated when they are not entailed by or satisfied in the context, and they can be locally accommodated (e.g., under the polar question operator) to avoid contradiction, uninformativity or problems with binding. Such analyses led us to expect that presuppositions are rated as natural in higher and lower prior probability contexts, as these contexts do not contradict the CCs, make the CCs uninformative, or lead to problems with binding. Contrary to this expectation, the CCs of the five purportedly factive predicates received lower ratings in the lower prior probability context than in the higher prior probability context.\footnote{In the higher prior probability context, our five purportedly factive predicates received ratings roughly comparable to the ratings of the factive predicates investigated in \citealt{mandelkern-etal2020} in their support context. Specifically, in our higher prior probability context, the mean naturalness ratings for the CCs of the five factive predicates ranged from .64 ({\em reveal}) to .78 ({\em know}) on a scale from 0 to 1. In \citepos{mandelkern-etal2020} support context, the CCs of {\em be aware} and {\em be happy} received mean naturalness ratings of about 4.4 and 4.7 out of 7 (based on Fig.~8 in their Appendix).} This result suggests that naturalness ratings are sensitive to the prior probability of content, such that an interrogative with a clause-embedding predicate is judged as more natural in a context in which the CC has a higher prior probability than in a context in which it has a lower prior probability.

This result has several methodological and theoretical implications. First, this result aligns with the result of \citealt{degen-tonhauser-openmind} based on an inference rating measure, suggesting that inference rating and naturalness rating measures are sensitive to some of the same factors. Second, naturalness ratings in explicit ignorance and support contexts are sensitive to a whole slew of factors, including the (implicit) prosody of the utterance and the defeasibility, at-issueness, and the prior probability of content. The assumption that naturalness ratings in such contexts distinguish presuppositions from nonpresuppositions cannot be maintained.
Finally, for analyses of presuppositions that assume a mechanism of local accommodation, the result means that local accommodation is sensitive to the prior probability of content, not just to whether the content is contradictory or uninformative in the context.

@@

As mentioned in \S\ref{s1}, \citealt{tbd-variability} observed that the CCs of factive predicates vary in how projective they are,  based on data collected with an inference rating measure. This observation led them to propose that projection is gradient rather than categorical. This proposal was further supported by the results of the experiments and analyses of existing datasets in \citealt{degen-tonhauser-language}, who found that the projection means of the CCs of factive and nonfactive predicates form a gradient rather than being categorically distinct (see Fig.~\ref{fig:dt1a}). \citealt{mandelkern-etal2020}, on the other hand, maintained that projection is categorical and  they claimed that  their naturalness rating measure categorically distinguishes presuppositions and nonpresuppositions.  As discussed above, neither the results presented in \citealt{mandelkern-etal2020} nor the results of our experiment empirically support the claim that projection is categorical. Instead, the results of our experiment provide further empirical support for the proposal that contents associated with different expressions (e.g., the CCs of {\em know, discover} and {\em confess}) do not either project or not project, but rather exhibit quite fine-grained variation in how projective they are.

@@

For many decades the term `presupposition' has served researchers well to refer to content with properties distinct from, for instance, entailments, conventional implicatures and conversational implicatures. However, over the past two decades, both empirical and theoretical research has pointed out that the set of contents typically referred to as presuppositions is not as homogenous as perhaps initially assumed, resulting in theoretical analyses of particular subsets and an understanding of multiple dimensions of empirical variation among this set of contents. Against this background, the claim in \citealt{mandelkern-etal2020} that there is an empirical measure that categorically distinguishes presuppositions from nonpresuppositions sparked hope that there might be, after all, a way of preserving the term `presupposition' as a well-defined notion in the way it has been traditionally used.  Unfortunately, the results of our experiment did not support this claim, instead providing further evidence for variation among the set of contents traditionally referred to as presuppositions. We suggest retiring the term `presupposition' or, at least, confining its use to a particular subtype of projective content, such as content associated with a strong contextual felicity constraint.

>>>>

Presuppositions are taken to typically project out of entailment-canceling environments like the scope of negation (e.g., \citealt{ccmg90}). While projection is often characterized as categorical (that is, content either typically projects or not), there is mounting empirical evidence that projection is gradient \jd{after everything that was said in the response letter about this no longer being the point of the paper, it seems very odd to lead with this issue in the abstract}, with content being more or less projective (e.g., \citealt{karttunen71b,xue-onea11,demarneffe-etal-sub23,tbd-variability,degen-tonhauser-language}). \citealt{mandelkern-etal2020} critically evaluated the inference rating measures on which this empirical evidence is based and claimed that a different measure, namely naturalness ratings in explicit ignorance contexts, provides support for categorical projection and distinguishes presuppositions from nonpresuppositions. This paper presents the results of an experiment designed to investigate \citepos{mandelkern-etal2020} claim for factive predicates (presumed presupposition triggers) and nonfactive ones (nontriggers). The results do not support \citepos{mandelkern-etal2020} claim and rather align with \citepos{degen-tonhauser-language} result that there is no evidence for a categorical distinction between factive and nonfactive predicates. \jd{ok yeah in general perhaps the abstract needs to be revised to accommodate the revised framing}

@@

\noindent
{\bf Keywords:} Presuppositions, categorical vs.\ gradient projection \jd{maintain this keyword or not?}, inference ratings, naturalness ratings in explicit ignorance contexts.

@@

Presuppositions are often characterized as backgrounded content that typically projects out of entailment-canceling environments, like the scope of negation or a polar interrogative (e.g., \citealt{ccmg90}).\footnote{Conventional implicatures also project out of these environments. They differ from presuppositions in that they contribute novel information. For discussion see, e.g., \citealt{ccmg90} and \citealt{potts05}.} For example, the content of the clausal complement (CC) of {\em know} in (\ref{first}a) is taken to be a presupposition because a speaker who utters (\ref{first}a) is typically taken to believe the CC, that Julian dances salsa, even though the CC occurs in a polar interrogative. By contrast, the CC of {\em think} in (\ref{first}b) is not assumed to be a presupposition because it does not typically project. Accordingly, {\em know} is analyzed as a presupposition trigger, but {\em think} is not.

@@

Most theoretical work assumes that projection is a categorical property of  content \jd{should there be references here?} --  that is, content either typically projects (in which case it is a presupposition) or it does not (in which case it is not a presupposition). There is, however, mounting empirical evidence that projection is not a categorical property of  content but rather a gradient one, with content being more or less projective \jd{again, i thought the response letter said that the gradience issue is no longer the main point of the paper. but it feels very central here.}. This evidence has been established using inference rating measures. Such measures involve presenting participants with an utterance (like (\ref{first}a)) and contents (like that Julian dances salsa), and asking for ratings that are taken to reveal the existence or strength of the inference to the content \jd{"being true"?}. \citealt{karttunen71b}, for instance, suggested that the CCs of {\em regret} and {\em discover}, which he took to be presuppositions, exhibit projection variability in examples like (\ref{kart}). Specifically, he suggested that a speaker who utters (\ref{kart}a) believes that the addressee has not told the truth, whereas a speaker who utters (\ref{kart}b) ``is not sure about the truth of the complement'' (p.63).

@@

\citealt[\S6.2]{mandelkern-etal2020} suggested that naturalness ratings of utterances in explicit ignorance contexts are better suited to distinguish presuppositions from nonpresuppositional projection inferences \jd{ok here is the pivot from the discussion of gradient vs categorical projection inferences to presuppositions vs nonpresuppositions. this doesn't feel concordant with the above. perhaps it's just a matter of introducing the right kind of bridge?}.\footnote{\citealt{mandelkern-etal2020} refer to the measure as an acceptability rating measure, but since participants were asked to rate the naturalness of utterances, we refer to it as a naturalness rating measure.} On this measure, participants are presented with utterances in which a speaker states that they are ignorant about a content, as in (\ref{mtrig}a), and then follows up with an utterance in which the content occurs embedded in an entailment-canceling environment, such as the antecedent of a conditional in (\ref{mtrig}c). \citealt{mandelkern-etal2020} assumed that if the content is a presupposition (such as the pre-state content of {\em stop} in (\ref{mtrig}c)), the utterance is rated as unnatural in the explicit ignorance context because presuppositions are contents that the speaker believes to be true. That is, in such constellations,  participants ``will not have an alternative to interpreting the presupposition at the utterance level, and in turn seeing the utterance as infelicitous and the speaker as incoherent'' (p.497).  If, on the other hand, the content is not a presupposition (such as the pre-state content of {\em now frown on} in (\ref{mtrig}c)), the utterance is assumed to be natural: Even if participants might in some context draw a projection inference ``for any of a variety of pragmatic reasons short of entailment or presupposition, [\ldots] they will tend to relinquish that inclination when there is pragmatic pressure to do so'', as in the explicit ignorance contexts (p.497). Both presupposition triggers and nontriggers were expected to be judged as natural in the support context, which entails the relevant content, illustrated in (\ref{mtrig}b).

@@

However, the empirical evidence in \citealt{mandelkern-etal2020} for their claim that projection is categorical \jd{the reviewers will point again to this being a strawman claim, no?} is weak. This is primarily because the goal of their work was not to investigate this claim,\jd{Reviewer 1 explicitly points out the issues with this argumentation} but whether presupposition projection in conjunctions is symmetric. It is also weak, however, because the results (shown in Fig.~8 in their Appendix 3) do not appear to support a categorical distinction between the presupposition triggers and nontriggers investigated, even though there were only four triggers ({\em be aware, be happy, stop, continue}) and four nontriggers ({\em now frown on, enjoy, hope, be sure}).  First, considering just the mean naturalness ratings in the explicit ignorance context, it appears that the ratings for the presuppositions and nonpresuppositions overlap: \jd{would be helpful to have the Mandelkern et al plot here} The ratings for the presuppositions ranged from 1 (for the pre-state of {\em continue}) to about 3.5 (for the CC of {\em be aware}), and the ratings for the nonpresuppositions range from just below 3 (for the CC of {\em hope}) to 4.5 (for the CC of {\em be aware}). It is therefore not clear that naturalness ratings in explicit ignorance contexts provide evidence for a categorical distinction between the four presuppositions and the four nonpresuppositions investigated in \citealt{mandelkern-etal2020}. Second, there is no consistent effect of context: Whereas the difference between the mean naturalness ratings in the explicit ignorance and support context was quite large for the (presuppositional) pre-state of {\em continue}, the difference was much less pronounced for the (presuppositional) CC of {\em be aware}, where it was roughly comparable to that of the (nonpresuppositional) pre-state of {\em frown on}. Thus, it is not clear that comparisons of ratings in support and explicit ignorance contexts provides empirical support for a categorical projection either. \jd{again, framing in terms of categorical/gradient projection}

@@

This paper presents the results of an experiment designed to investigate \citepos{mandelkern-etal2020} claim that the measure they proposed provides evidence that projection is categorical \jd{categorical projection issue} and distinguishes presuppositions from nonpresuppositions.\footnote{\label{f:github}The experiment was approved by the ethics review committee of [university name suppressed]. The experiment, materials, data, and analysis scripts can be accessed here:  \url{https://anonymous.4open.science/r/naturalness-in-EIC-5847}.}  To allow for comparison with the results of \citealt{degen-tonhauser-language}, \jd{why is that comparison relevant/important?} the CCs of the same 20 (non)factive clause-embedding predicates (see Fig.~\ref{fig:dt1a}) were investigated. The experiment also included control stimuli with {\em stop, continue, again, too, also}, and an {\em it-}cleft to allow for comparison with the results of \citealt{mandelkern-etal2020} and the assumptions made in \citealt{simons01} and \citealt{abusch10}.

The design of \citepos{mandelkern-etal2020} Exp.~3 was slightly modified to allow for comparison with the result of \citealt{degen-tonhauser-openmind} that the projection of content is sensitive to the content's prior probability \jd{again, why are we interested in that comparison? how does it inform the research question?}. Specifically, what \citealt{degen-tonhauser-openmind} found was that the higher the prior probability of a content, the stronger the projection inference. For instance, a speaker's commitment to the CC of (\ref{prior}c), that Julian dances salsa, was stronger in the context in (\ref{prior}b), where the CC has a higher prior probability, than in the context in (\ref{prior}a), where the CC has a lower prior probability.

@@

In addition to the 1,200 target stimuli (400 interrogatives $\times$ 3 contexts), the materials also included the six control stimuli in (\ref{filler}). The interrogatives of the control stimuli featured six expressions typically analyzed as presupposition triggers, namely {\em stop, continue, again, too, also}, and an {\em it-}cleft. The preceding declaratives conveyed the speaker's explicit ignorance about the presuppositions associated with these expressions.\footnote{The contents investigated for {\em too} and {\em also} in (\ref{filler}d) and (\ref{filler}e) are that Ann plays an instrument other than the flute and that Svenja plays a sport other than soccer. This interpretation arises if {\em too} and {\em also} associate with {\em the flute} and {\em soccer}, respectively. While prosody was not controlled for, this focus association is made plausible by the preceding explicit ignorance statements, which evoke the question of whether Ann plays any instrument and whether Svenja plays any sport, respectively.} Two of these expressions, namely {\em stop} and {\em continue}, were target expressions in \citepos{mandelkern-etal2020} Exp.~3, where they were assumed to be unnatural in explicit ignorance contexts. This is in contrast to \citealt{simons01}, who took {\em stop} to be a soft trigger that is natural in explicit ignorance contexts. Three expressions were assumed to be unnatural in explicit ignorance contexts in \citealt{simons01} ({\em again}) and \citealt{abusch10} ({\em too}, {\em it-}cleft). The control stimuli were included for comparison to the target stimuli, to the claims of \citealt{simons01} and \citealt{abusch10}, and to the results of \citealt{mandelkern-etal2020}. \jd{to the reviewer's point that these are not controls: wrong. but make clear how they function as controls, ie what their conceptual purpose is.}

@@

\paragraph{Results.} Recall that \citealt{simons01} and \citealt{abusch10} assumed that only hard presuppositions are unnatural in explicit ignorance contexts, whereas \citealt{mandelkern-etal2020} assumed that all presuppositions are unnatural in such contexts. Figure \ref{fig:acc-by-expression} shows mean naturalness ratings in the explicit ignorance context by expression (in distinct colors: \color{orange}factive predicates\color{black}, \color{green}nonfactive predicates\color{black},  controls). As shown, the purported presupposition triggers, that is, the controls and the factive predicates, do not exhibit a unified pattern: The means of four controls ({\em continue, too, also, again}) are at floor, those of {\em stop} and {\em be annoyed} are slightly higher, those of the {\em it-}cleft and {\em know} are higher again, but lower than those of {\em see} and {\em discover}, and, finally, those of {\em reveal} are highest. We also see that the naturalness ratings of {\em see, discover} and {\em reveal} are just as high as those of some nonfactive predicates. These results do not provide empirical support for a categorical distinction between presuppositions and nonpresuppositions \jd{let's talk through this again from the reviewers' perspective?}, contrary to what \citealt{mandelkern-etal2020} claimed. These results also do not provide support for a class of factive predicates that is categorically distinct from nonfactive ones, in line with the result of \citealt{degen-tonhauser-language} based on inference rating measures.

@@

The linking function \jd{"function" is a strong word here, perhaps "linking assumption"?} assumed in \citealt{mandelkern-etal2020} is that presupposition triggers \jd{"sentences with presupposition triggers"?} are rated as unnatural in contexts in which the speaker is explicitly ignorant of the presupposed content, and that nontriggers are rated as natural in such contexts. This linking function is challenged by some of the results of our experiment \jd{or perhaps people were just wrong about the classification?}. Consider first the CC of {\em be annoyed}, which received a very low mean naturalness rating in the explicit ignorance context. Under \citepos{mandelkern-etal2020} linking function, one can make sense of this result by analyzing the CC of {\em be annoyed} as being conventionally coded as having to be entailed by or satisfied in the common ground of the interlocutors. It has been long known, however, that such an analysis is not tenable for emotive predicates like {\em be annoyed}, as they do not presuppose that the CC is part of the common ground of the interlocutors but merely that the attitude holder believes the CC to be true (e.g., \citealt{heim92,karttunen2016}). In (\ref{emo}), for instance, the speaker does not believe that Sue could stay in bed.

@@

The results for {\em know} also challenge \citepos{mandelkern-etal2020} linking function. As shown in Fig.~\ref{fig:acc-by-expression}, the naturalness ratings for the CC of {\em know} exhibit a bimodal pattern, with about half of the participants rating it as relatively unnatural in the explicit ignorance context and about half as relatively natural. For the first group of participants, one could assume either that they reacted to the contradiction between the speaker's explicit ignorance statement and the inference arising from the interrogative that the CC projects to the common ground of the interlocutors, or one could assume an analysis along the same lines as for {\em be annoyed} above as the CC of {\em know} is also highly not-at-issue (\citealt{tbd-variability}). For the second group of participants, those who judged speakers' utterances like (\ref{pros}) as fairly natural, one hypothesis is that they read the utterances with a (possibly implicit) prosody that supports an interpretation on which the CC does not project out of the interrogative utterance. Two possible prosodies are indicated by the ToBI transcriptions  in (\ref{pros}); in both, the interrogative is realized with the so-called rise-fall-rise contour.\footnote{ToBI refers to the Tones and Break Indices annotation system of \citealt{beckman-ayers97}. In this system, L*+H identifies a pitch accent whose low target is aligned with the stressed syllable and which is followed by a trailing high target. A L* pitch accent may also be followed by a low (L-) or high (H-) intermediate phrase tone. An intonational phrases may end with a low intermediate phrase tone and a high intonational phrase tone (L-H\%) or a high intermediate and intonational phrase tone (H-H\%).}

@@

As shown, the effect of context is not uniform for the factive predicates. For {\em be annoyed} and {\em know} the mean naturalness rating is quite a bit lower in the explicit ignorance context than in the higher prior probability context, whereas the difference is much less pronounced for {\em see} and {\em discover}, and not observed for {\em reveal}. This last pattern is also observed for several nonfactive predicates, including {\em confess, hear, announce}, and {\em be right}. Thus, naturalness ratings in explicit ignorance vs.\ higher prior probability contexts do not provide support for a categorical distinction between the CCs of factive and nonfactive predicates. A comparison between the explicit ignorance and lower prior probability contexts also suggests differences between the factive predicates: Whereas for {\em be annoyed} the mean naturalness rating is lower in the explicit ignorance context than in the lower prior probability context, the two means are equally high for {\em know}, but the rating in the lower prior probability context is lower than that in the explicit ignorance context for {\em see, discover}, and {\em reveal}. This last pattern is observed for all of the nonfactive predicates. Thus, naturalness ratings in explicit ignorance vs.\ lower prior probability contexts also do not provide support for a categorical distinction between the CCs of factive and nonfactive predicates. \jd{this paragraph contains a lot of "categorical distinction" prose}

@@

\paragraph{Discussion.} As mentioned above, contemporary presupposition analyses (e.g., \citealt{heim83,vds92}) assume that presuppositions are by default globally accommodated when they are not entailed by or satisfied in the context, and they can be locally accommodated (e.g., under the polar question operator) to avoid contradiction, uninformativity or problems with binding. Such analyses led us to expect that presuppositions are rated as natural in higher and lower prior probability contexts, as these contexts do not contradict the CCs, make the CCs uninformative, or lead to problems with binding. \jd{nice. i'm not sure this prediction/expectation was explicitly stated at the outset, but is very much worth stating.} Contrary to this expectation, the CCs of the five purportedly factive predicates received lower ratings in the lower prior probability context than in the higher prior probability context.\footnote{In the higher prior probability context, our five purportedly factive predicates received ratings roughly comparable to the ratings of the factive predicates investigated in \citealt{mandelkern-etal2020} in their support context. Specifically, in our higher prior probability context, the mean naturalness ratings for the CCs of the five factive predicates ranged from .64 ({\em reveal}) to .78 ({\em know}) on a scale from 0 to 1. In \citepos{mandelkern-etal2020} support context, the CCs of {\em be aware} and {\em be happy} received mean naturalness ratings of about 4.4 and 4.7 out of 7 (based on Fig.~8 in their Appendix).} This result suggests that naturalness ratings are sensitive to the prior probability of content, such that an interrogative with a clause-embedding predicate is judged as more natural in a context in which the CC has a higher prior probability than in a context in which it has a lower prior probability.

This result has several methodological and theoretical implications. First, this result aligns with the result of \citealt{degen-tonhauser-openmind} based on an inference rating measure, suggesting that inference rating and naturalness rating measures are sensitive to some of the same factors. Second, naturalness ratings in explicit ignorance and support contexts are sensitive to a whole slew of factors, including the (implicit) prosody of the utterance and the defeasibility, at-issueness, and the prior probability of content.  \jd{the reviewer is right that sensitivity to this "slew of factors" is presented as fact/as following from the experiment, but it's really only the prior effect that's directly shown. should revise} The assumption that naturalness ratings in such contexts distinguish presuppositions from nonpresuppositions cannot be maintained.
Finally, for analyses of presuppositions that assume a mechanism of local accommodation, the result means that local accommodation is sensitive to the prior probability of content, not just to whether the content is contradictory or uninformative in the context.

@@

\jd{if this is no longer the point of the paper, why is it here?}
As mentioned in \S\ref{s1}, \citealt{tbd-variability} observed that the CCs of factive predicates vary in how projective they are,  based on data collected with an inference rating measure. This observation led them to propose that projection is gradient rather than categorical. This proposal was further supported by the results of the experiments and analyses of existing datasets in \citealt{degen-tonhauser-language}, who found that the projection means of the CCs of factive and nonfactive predicates form a gradient rather than being categorically distinct (see Fig.~\ref{fig:dt1a}). \citealt{mandelkern-etal2020}, on the other hand, maintained that projection is categorical and  they claimed that  their naturalness rating measure categorically distinguishes presuppositions and nonpresuppositions.  As discussed above, neither the results presented in \citealt{mandelkern-etal2020} nor the results of our experiment empirically support the claim that projection is categorical. Instead, the results of our experiment provide further empirical support for the proposal that contents associated with different expressions (e.g., the CCs of {\em know, discover} and {\em confess}) do not either project or not project, but rather exhibit quite fine-grained variation in how projective they are.

@@

For many decades the term `presupposition' has served researchers well to refer to content with properties distinct from, for instance, entailments, conventional implicatures and conversational implicatures. However, over the past two decades, both empirical and theoretical research has pointed out that the set of contents typically referred to as presuppositions is not as homogenous as perhaps initially assumed, resulting in theoretical analyses of particular subsets and an understanding of multiple dimensions of empirical variation among this set of contents. Against this background, the claim in \citealt{mandelkern-etal2020} that there is an empirical measure that categorically distinguishes presuppositions from nonpresuppositions sparked hope that there might be, after all, a way of preserving the term `presupposition' as a well-defined notion in the way it has been traditionally used.  Unfortunately, the results of our experiment did not support this claim, instead providing further evidence for variation among the set of contents traditionally referred to as presuppositions. We suggest retiring the term `presupposition' \jd{stands in conflict with what is stated in the response letter} or, at least, confining its use to a particular subtype of projective content, such as content associated with a strong contextual felicity constraint.
